Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-19 stp/paper_aaai/main.tex
Experiments section partially

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. We
use the term ``appropriate'' since there might be many such triples which are
well-formed source descriptions, but only one or a few will capture the intended
meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} from the semantic model 
$m^\star$ to the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

@@

To provide an integrated view over the known sources descriptions $S_T$, we 
need to align their semantic models as well as all considered semantic 
types. This is achieved by constructing an \emph{alignment graph}.

@@

The algorithm we used to construct $\mathcal{G_O}$ is the same as Taheriyan 
\etal{} and is described in detail in the cited paper 
\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

@@

An example alignment graph is illustrated in Fig. \ref{FIG:ali}. 
Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching}

This tool provides us with a list of patterns that are frequent, as well as 
their support. 
The \emph{support} of a pattern is a measure of frequency. 
Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.

@@

We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).

@@

We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics}

@@

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
\npr{Explain}

\begin{table}[t]\small
  \centering
  \caption{Average performance of semantic labeling for leave one out strategy.}
  	\label{tab:unknownloo}
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{numBags}},
		    ylabel={Performance (MRR)},
		    xmin=0, xmax=150,
		    ymin=0.5, ymax=1,
		    xtick={0,10,50,100,150},
		    ytick={0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (10, 0.85154623154623166)(50, 0.85902097902097896)(100,0.87487956487956486)(150,0.8802331002331002)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (10,  0.73272601851632158)(50, 0.73596072887032105)(100,0.73736629035127532)(150,0.73512315058140676)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (10,  0.53396973928187841)(50, 0.56218126081141884)(100,0.55857468339226135)(150,0.55938671902457904)
		    };
		 \addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (10,  0.81292733659634253)(50, 0.81182668838989458)(100, 0.80705336361770219)(150,0.80801980454223066)
		    };
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (10,   0.87823326846764416)(50, 0.89727564102564272)(100,0.9136698717948738)(150,0.91708333333333425)
		    };
		%\legend{weather,weapons,soccer,museum,city}

		\end{axis}
\end{tikzpicture}
\subcaption{fixing \emph{bagSize}=100}\label{fig:numbags}
\end{minipage}%
%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline]
		\begin{axis}[
		    xlabel={\emph{bagSize}},
		    %ylabel={Performance (MRR)},
		    xmin=0, xmax=100,
		    ymin=0.5, ymax=1,
		    xtick={0,10,30,50,100},
		    ytick={0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=outer north east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (10, 0.88427350427350415)(30,  0.9027583527583527)(50,0.91336441336441332)(100,0.87871794871794873)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (10,  0.75910921069769555)(30, 0.76156533626682754)(50,0.75502218858295522)(100,0.75538165183154382)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (10,  0.56646107828012637)(30, 0.5693901714881866)(50,0.58629781920572777)(100,0.58408351395802571)
		    };
		 \addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (10,  0.78552344907839267)(30, 0.78870711278952932)(50,0.78519302797324753)(100,0.77792094596490047)
		    };
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (10,  0.80810421349483996)(30, 0.84745259081196467)(50,0.8751719894688631)(100,0.89739411630036825)
		    };
		\legend{weather,weapons,soccer,museum,city}

		\end{axis}
	\end{tikzpicture}
\subcaption{fixing \emph{numBags}=50}\label{fig:bagsize}
\end{minipage}
\caption{Average precision and recall on museum domain.}\label{fig:bagging}
\end{figure*}

\section{Related Work \label{SEC:pw}}
\ddg{rewrite, add more}
\npr{Now the opposite: shrink please}

>>>>

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. 
We
use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, but only one or a few will capture the intended meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

@@

To provide an integrated view over the known source descriptions $S_T$, we 
need to align their semantic models as well as all considered semantic 
types. 
This is achieved by constructing an \emph{alignment graph}.

@@

The algorithm we used to construct $\mathcal{G_O}$ is the same as \cite{taheriyan2016learning} and is described in detail in their work.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

@@

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. 
This is 
known as the Frequent Graph Pattern Mining, which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining~\cite{yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}

This tool provides us with a list of patterns that are frequent, as well as 
their support. 
The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.

@@

% datasets for evaluation
We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).
The museum dataset~\cite{taheriyan2016learning} contains 29 sources which are mapped to the EDM domain ontology.
The soccer dataset~\cite{Pham:semantic} is much smaller with only 12 data sources, and its domain ontology is an extension of the schema.org ontology.

@@

% baseline for evaluation
We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
However, they use approximation algorithms both for the matching and for the STP parts.
Additionally, they do not consider unmatched attributes in the sources.
To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.

% performance metrics
The performance of these systems is estimated in terms of \emph{precision} and \emph{recall}.
Assuming $m^\star$ is the predicted semantic model and $m^\dag$ is the correct semantic model, then:
$$precision = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\star)|}$$
$$recall = \frac{|rel(m^\star)\cap rel(m^\dag)|}{|rel(m^\dag)|}$$
where $rel(m)$ is the set of triples $(u,e,v)$ with $e$ being an edge from the vertex $u$ to the vertex $v$ in the semantic model $m$.
Since we want to estimate the accuracy of both the matching and STP parts,
we also include triples for attributes and data nodes into the corresponding sets.
Note that unmatched attributes as well as \emph{unknown} and \emph{root} nodes are not part of these sets.
We perform also a modification to the ground truth semantic models:
if the true semantic label of an attribute is not present in any of the previously mapped data sources,
we substitute it with \emph{unknown} and map it to the \emph{Unknown} class node.
In such way we validate how well the systems can detect earlier unseen cases.

% semantic labeling models
To illustrate that our semantic labeling model is better suited for the
matching task, we compare it against the state-of-the-art model \emph{DSL}~\cite{Pham:semantic} which was shown to perform even better than SemanticTyper. 
\npr{not sure whether I should explain how this model works}
We use \emph{mean reciprocal rank} (MRR) to evaluate semantic labeling models.
This measure is useful to estimate how highly the true semantic label is ranked among top $k$ suggestions.
It is calculated the following way:
$$MRR = \frac{1}{n}\sum_{i=1}^{n}{\frac{1}{rank_i}},$$
where $rank_i$ is the rank of the correct semantic label for the attribute $a_i$ among the top $k$ predictions.

% evaluation strategy
We perform an evaluation strategy outlined by~\cite{taheriyan2016learning}.
Let $M_j$ be the set of $j$ known semantic models.
For each data source $s_i$ in the domain we perform experiments $t-1$ times,
where $t$ is the total number of data sources in the domain and each experiment has a different number of known semantic models $M_1, M_2, \ldots, M_{t-1}$.
The case with $M_{t-1}$ known semantic models corresponds to leave-one-out validation strategy. 
For example, in the soccer domain for the source $s_1$ we run experiments 11 times using $M_1=\{m_2\}, M_2=\{m_2, m_3\}, \ldots, M_{11}=\{m_2, m_3, \ldots, m_{12}\}$
We repeat the procedure for other data sources in the domain and then average the results.
Such procedure ensures that each source is at least once in the training as well as testing datasets.

% architecture
We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics, AWS machine is bigger}

@@

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
\npr{Explain}

\begin{table}[t]\small
  \centering
  \caption{Average performance of semantic labeling models for leave one out strategy.}
  	\label{tab:semlab}
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

%%%
% performance figures
%%%
We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.

%%% museum domain
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={Performance},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.477688172043011)(2,0.543722761679028)(3,0.584279525763794)(4,0.560916442048518)(5,0.508442559100454)(6,0.451911027568922)(7,0.560410216718266)(8,0.627540834845735)(9,0.658907184769254)(10,0.494298245614035)(11,0.594547996272134)(12,0.572438909774436)(13,0.643132689678742)(14,0.544147521036133)(15,0.561388900346478)(16,0.620470013199142)(17,0.631330163644405)(18,0.644192377495463)(19,0.642924629016761)(20,0.656325397672681)(21,0.610482642157672)(22,0.628992740471869)(23,0.570074611816898)(24,0.679169187336157)(25,0.673558897243108)(26,0.667890182643746)(27,0.68742147145051)(28,0.709820528332325)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.570063795853269)(2,0.756845238095238)(3,0.621034680606911)(4,0.719615829557505)(5,0.663677414539484)(6,0.680661881977671)(7,0.702849371292569)(8,0.730720679999118)(9,0.715323491375385)(10,0.722695511010729)(11,0.722586065299008)(12,0.725508681952266)(13,0.728214414334958)(14,0.753560036454773)(15,0.778231825645619)(16,0.745982043507288)(17,0.715855206037534)(18,0.733838894506235)(19,0.728435738081271)(20,0.754932383250967)(21,0.76774421230943)(22,0.761660230839754)(23,0.750358005521049)(24,0.82098385331144)(25,0.823507591442374)(26,0.834847535505431)(27,0.84013108540293)(28,0.813133718212162)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.580144743457437)(2,0.699277168494516)(3,0.596982860940987)(4,0.683431847315197)(5,0.634133314342686)(6,0.630169810336433)(7,0.628025663269931)(8,0.642973856209151)(9,0.618457602339181)(10,0.616241290282443)(11,0.606940556177678)(12,0.605471976942706)(13,0.598988030767536)(14,0.608112237561116)(15,0.609841319882303)(16,0.578626150272492)(17,0.55776862026862)(18,0.57760989010989)(19,0.567994505494506)(20,0.492368742368742)(21,0.582722832722833)(22,0.574786324786325)(23,0.644688644688645)(24,0.658424908424909)(25,0.708791208791209)(26,0.716727716727717)(27,0.719373219373219)(28,0.708791208791209)
		    };
		%\legend{karma,serene,serene-pats}

		\end{axis}
\end{tikzpicture}
\subcaption{precision}\label{fig:museumprec}
\end{minipage}%
%
\begin{minipage}[b]{.33\linewidth}
\centering
\begin{tikzpicture}[baseline]
		\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={recall},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    ymajorgrids=true,
		    grid style=dashed,
		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.209547221954433)(2,0.411561264822134)(3,0.457295783926219)(4,0.449720026350461)(5,0.414575098814229)(6,0.364575098814229)(7,0.452173913043478)(8,0.526317523056654)(9,0.588158761528327)(10,0.403491436100132)(11,0.506175889328063)(12,0.489690382081687)(13,0.584008563899868)(14,0.470553359683795)(15,0.48570487483531)(16,0.553513584117033)(17,0.553774817136886)(18,0.573236677115987)(19,0.567816091954023)(20,0.580551201671891)(21,0.557301462904911)(22,0.559979101358412)(23,0.477098571926158)(24,0.57088122605364)(25,0.56078021595263)(26,0.565134099616858)(27,0.585336119818878)(28,0.598310693138279)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.558240946045824)(2,0.733876811594203)(3,0.610770750988142)(4,0.707559288537549)(5,0.654891304347826)(6,0.670421607378129)(7,0.704710144927536)(8,0.729611330698287)(9,0.716913702239789)(10,0.728837285902504)(11,0.724769433465085)(12,0.724670619235837)(13,0.727783267457181)(14,0.76187417654809)(15,0.790283267457181)(16,0.751266980146291)(17,0.72991118077325)(18,0.761259143155695)(19,0.742058516196448)(20,0.759103970741902)(21,0.776149425287357)(22,0.758842737722048)(23,0.730668756530825)(24,0.800330895158482)(25,0.800330895158482)(26,0.808951584813654)(27,0.813305468477882)(28,0.790229885057471)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.571875702946753)(2,0.770701581027668)(3,0.637285902503294)(4,0.73596837944664)(5,0.677618577075099)(6,0.693148880105402)(7,0.725263504611331)(8,0.750164690382082)(9,0.739640974967062)(10,0.743988801054019)(11,0.742094861660079)(12,0.734420289855072)(13,0.742934782608696)(14,0.775131752305666)(15,0.795965085638999)(16,0.772361546499478)(17,0.752899686520376)(18,0.776671891327064)(19,0.765308254963427)(20,0.733838383838384)(21,0.783986415882968)(22,0.774255485893417)(23,0.751219087425984)(24,0.803030303030303)(25,0.828456983629397)(26,0.83707767328457)(27,0.841431556948798)(28,0.828456983629397)
};
		 %\legend{karma,serene,serene-pats}

		\end{axis}
	\end{tikzpicture}
\subcaption{recall}\label{fig:museumrec}
\end{minipage}%
%
\begin{minipage}[b]{.33\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={time(s)},
		    xmin=1, xmax=28,
		    ymin=0.0, ymax=8.5,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.0,1,2,3,4,5,6,7,8},
		    ymajorgrids=true,
		    grid style=dashed,
		    %legend pos=outer north east,
		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.28413987159729)(2,0.598592698574067)(3,0.36263108253479)(4,0.400362551212311)(5,0.387216985225677)(6,0.392432987689972)(7,0.394440889358521)(8,0.430805265903473)(9,0.438177883625031)(10,0.441894292831421)(11,0.461780428886414)(12,0.469180881977081)(13,0.477133095264435)(14,0.498149693012238)(15,0.512342214584351)(16,0.600962460041046)(17,0.5725257396698)(18,0.907191514968871)(19,0.551609396934509)(20,0.585879027843475)(21,0.610454380512239)(22,0.575962841510773)(23,0.657813549041748)(24,0.671637773513794)(25,0.689822912216188)(26,0.724388360977171)(27,0.750569899876912)(28,0.771229823430379)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.0166666666666667)(2,0.995)(3,0.8725)(4,0.8325)(5,0.9175)(6,0.965)(7,0.89)(8,0.9675)(9,0.96)(10,1.1225)(11,1.1475)(12,1.36)(13,1.295)(14,1.3925)(15,1.375)(16,1.4975)(17,1.9575)(18,2.11)(19,1.9075)(20,1.9175)(21,1.865)(22,1.915)(23,2.49)(24,2.4)(25,2.49)(26,2.49)(27,2.68333333333333)(28,2.47666666666667)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.025)(2,1.0375)(3,0.93)(4,1)(5,0.9575)(6,0.9425)(7,0.9)(8,0.975)(9,1.06)(10,1.2025)(11,1.2975)(12,1.9425)(13,1.52)(14,2.2825)(15,1.6275)(16,3.5375)(17,2.255)(18,2.1625)(19,6.505)(20,1.44666666666667)(21,2.2825)(22,2.3475)(23,8.28666666666667)(24,1.895)(25,8.3)(26,3.75333333333333)(27,3.73)(28,3.75)
};
		 %\legend{karma,serene,serene-pats}

		\end{axis}
\end{tikzpicture}
\subcaption{time (s)}\label{fig:museumtime}
\end{minipage}%
\caption{Average precision, recall and time on the museum domain for \relonto{} systems with variable training set size.}\label{fig:perfmuseum}
\end{figure*}

%%% soccer domain
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={Performance},
		    xmin=1, xmax=11,
		    ymin=0.5, ymax=0.9,
		    xtick={1,2,4,6,8,10,11},
		    ytick={0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.635191626901633)(2,0.549997502815009)(3,0.675720834727361)(4,0.719693253328935)(5,0.759169846724195)(6,0.760054331456753)(7,0.800812140122402)(8,0.812192030050689)(9,0.799552066440611)(10,0.821470975418344)(11,0.785878855002637)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.676934852587026)(2,0.61473599870339)(3,0.723937079602602)(4,0.786238815638129)(5,0.777035817669233)(6,0.781984613615049)(7,0.81368099248534)(8,0.817013725291758)(9,0.816270530687007)(10,0.846744827831784)(11,0.852649148301322)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.66759959719914)(2,0.629014687197419)(3,0.692208378950833)(4,0.744652988406557)(5,0.773486992410165)(6,0.756607637648352)(7,0.803820434917082)(8,0.793054493090329)(9,0.792256229657042)(10,0.822093203062231)(11,0.828181360184871)
		    };
		%\legend{karma,serene,serene-pats}

		\end{axis}
\end{tikzpicture}
\subcaption{precision}\label{fig:soccerprec}
\end{minipage}%
%
\begin{minipage}[b]{.33\linewidth}
\centering
\begin{tikzpicture}[baseline]
		\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={recall},
		    xmin=1, xmax=11,
		    ymin=0.3, ymax=0.9,
		    xtick={1,2,4,6,8,10,11},
		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    ymajorgrids=true,
		    grid style=dashed,
		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.444761527680188)(2,0.372447158105053)(3,0.545528381345078)(4,0.596008831526073)(5,0.6499887923799)(6,0.643884492868159)(7,0.685035675993026)(8,0.702870161195933)(9,0.654001538724769)(10,0.685153350715964)(11,0.662999993217779)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.690636806043505)(2,0.613080486764697)(3,0.72563707600459)(4,0.780625908674911)(5,0.776616927805676)(6,0.779496772132888)(7,0.813459305700685)(8,0.813245834960899)(9,0.810586300672508)(10,0.84298404022542)(11,0.849899398175261)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.689786194666577)(2,0.655399210040359)(3,0.719915653815835)(4,0.776231754935929)(5,0.802770096610387)(6,0.787355423564135)(7,0.838616573256072)(8,0.82175912881902)(9,0.821414409345444)(10,0.851497334083541)(11,0.85656084018153)
		    };
		 \legend{karma,serene,serene-pats}

		\end{axis}
	\end{tikzpicture}
\subcaption{recall}\label{fig:soccerrec}
\end{minipage}%
%
\begin{minipage}[b]{.33\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={time(s)},
		    xmin=1, xmax=11,
		    ymin=0.0, ymax=0.3,
		    xtick={1,2,4,6,8,10,11},
		    ytick={0.0,0.1,0.2},
		    ymajorgrids=true,
		    grid style=dashed,
		    %legend pos=outer north east,
		    %legend style={at={(0.5,-0.1)},anchor=north, legend columns=-1}
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.107354099100286)(2,0.137003461519877)(3,0.163627962271372)(4,0.17774627606074)(5,0.179288367430369)(6,0.183507978916168)(7,0.189805428187052)(8,0.191188136736552)(9,0.196139633655548)(10,0.200133164723714)(11,0.218581974506378)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.0595748017051003)(2,0.0895205450057983)(3,0.0976518734296163)(4,0.103216880957286)(5,0.108438626130422)(6,0.115763804117839)(7,0.125697635014852)(8,0.118865826924642)(9,0.119359710216522)(10,0.123752357959747)(11,0.153613630930583)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.0687879033522172)(2,0.0874820310419256)(3,0.103948153495789)(4,0.104214943885803)(5,0.115242712974548)(6,0.126150580406189)(7,0.122052125063809)(8,0.128753701051076)(9,0.129606107076009)(10,0.13165650844574)(11,0.142413517634074)
		    };
		 %\legend{karma,serene,serene-pats}

		\end{axis}
\end{tikzpicture}
\subcaption{time (s)}\label{fig:soccertime}
\end{minipage}%
\caption{Average precision, recall and time on the soccer domain for \relonto{} systems with variable training set size.}\label{fig:perfsoccer}
\end{figure*}

%%
As mentioned previously, the chuffed solver outputs solutions as it finds them.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
In all our experiments we use a timeout threshold of 15s for the chuffed solver.
Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
i.e., costs of patterns are scaled by a factor. 
%% sequentially found solutions and different weights for patterns
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{solution}},
		    ylabel={Performance},
		    xmin=0, xmax=20,
		    ymin=0.7, ymax=1,
		    xtick={0,5,10,15,20},
		    ytick={0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (0,0.813133718212162)(1,0.870689655172414)(2,0.869565217391304)(3,0.854700854700855)(4,0.847457627118644)(5,0.862068965517241)(6,0.862068965517241)(7,0.860869565217391)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (0,0.708791208791209)(1,0.720429778415431)(2,0.727852084972463)(3,0.734756097560976)(4,0.737969058591178)(5,0.723003960808839)(6,0.727905921593153)(7,0.740887177292826)(8,0.733003960808839)(9,0.746193299741805)(10,0.73554304773817)(11,0.74569890495285)(12,0.756325773784054)(13,0.745676961413577)(14,0.753615746683783)(15,0.7306060898002)(16,0.723882805154582)(17,0.720774744968293)(18,0.733079110976868)(19,0.731544715447155)(20,0.734034752112227)
